Are Lower Income Communities Given More Noise Exemptions

### 2024-09-24 paper/paper.qmd
edited dicussion

A ward's population was also found to be associated with a ward's number of noise exemptions. The relationship is understandable because ward's with more people will have more activities and more construction to meet the needs of those people, so it makes sense to have those permits.

## Weaknesses and Next Steps

>>>>

A ward's population was also found to be associated with a ward's number of noise exemptions. The relationship is understandable because ward's with more people will have more activities and more construction to meet the needs of those people, so it makes sense to have those permits. This might invalidate the finding that more median income has a positive relationship with number of permits for a ward if there is a relationship with population and ward medium income: and there is a moderate positive relationship. However, after removing the potential outliers (ward 10, 11, and 13) there appears to me no relationship between the two variables. Therefore, further explore would need to be done to fix determine whether or no this is a confounding relationship. See section @sec-weaknessnextsteps for more dicussion on confounding variables.

## Weaknesses and Next Steps {#sec-weaknessnextsteps}
